\TheTitle

### 2017-07-03 paper/results.tex
Results: Starting user opinion

Users were able to more closely estimate the number of commits and
merges in the larger tree, but generally took longer than the smaller
tree. The tree with a single node resulted in more variability in the
estimate of number of commits .

@@

>>>>

Users were able to more closely estimate the number of commits and
merges in the larger tree, but generally took longer than the smaller
tree. The tree with a single node resulted in more variability in the
estimate of number of commits.

@@

\subsection{User Opinions}
\label{sub:user_opinions}

There was nearly unanimous preference for \tool to the representation
provided by Gitk, citing the ability to abstract information about the
repository from the simple summarization tables and clean visualization.
Three of the twelve participants suggested that with better
understanding of the Gitk interface and of the DAG, that an expert may
be able to extract the summarization information with relative ease. Of
these three, one participant said that they would prefer to use both
tools side-by side. Further discussion on this is available in section
... %TODO Provide section.
